MSDS 7333 Case Study 06

### 2017-06-17 MSDS7333_CaseStudy06_MBaldree_BBrock_TElkins_AKelly.Rmd
updates

### Assignment: 
1. Conduct a more thorough data analysis into these two MAC addresses, including determining locations by using data corresponding to both: 
    + chosenAP = "00:0f:a3:39:e1:c0"
    + rejectedAP = "00:0f:a3:39:dd:cd"
* *Which of these two MAC addresses should be used and which should not be used for Real Time Location Services (RTLS)?*
* *Which MAC address yields the best prediction of location?including determining locations by using data corresponding to both MAC addresses*
* *Does using data for both MAC addresses simultaneously yield more, or less accurate prediction of location?*

@@

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

### Assignment: 
1. Conduct a more thorough data analysis into these two MAC addresses, including determining locations by using data corresponding to both: 
    + chosenAP = "00:0f:a3:39:e1:c0"
    + rejectedAP = "00:0f:a3:39:dd:cd"
* *Which of these two MAC addresses should be used and which should not be used for Real Time Location System (RTLS)?*
* *Which MAC address yields the best prediction of location?including determining locations by using data corresponding to both MAC addresses*
* *Does using data for both MAC addresses simultaneously yield more, or less accurate prediction of location?*

@@

## Introduction

## The Approach (Explained)

### Preliminary Functions to be used:

## The Output Achieved (this should be included as close as possible to the output or figures as possible)
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
